Pipit on the Post: Proving Pre- and Post-conditions of Reactive Systems

### 2023-12-16 2024pipit/Main.tex
ok

% checked box
\usepackage{wasysym}

@@

@@

>>>>

% checked box
\usepackage{wasysym}
\usepackage{underscore}

@@

Big TODOs:
\begin{itemize}
  \item example: trigger-fetch from ttcan;
  \item transition systems and translation;
  \item C codegen: note about duplicating work, sketch potential solution;
  \item C codegen: future work: sketch potential solution for separate compilation, compare to Accelerate FFI \cite{clifton2014embedding};
  \item cite Liam \cite{oconnor2019deferring} similar idea, but we defer the \emph{context} rather than just syntactically deferring the proof;
  % \item 
\end{itemize}

@@

\section{Time-triggered}

% \newcommand\signal{\textit{signal}}
\begin{tabbing}
  @MM@\= @MM@ \= \kill
  @let@ count_when ($\textit{limit}$: $\NN$) ($\textit{inc}$: stream $\BB$): stream $\NN$ = \\
    \> @let rec@ $\textit{count}$ @=@ \\
    \> \> @if@ $\textit{count} >= \textit{limit}$ @then@ $\textit{limit}$ \\
    \> \> @else@ $(0~@fby@~\textit{count}) + (@if@~\textit{inc}~@then@~1~@else@~0)$ \\
    \> @in@ $\textit{count}$ \\
\end{tabbing}

\begin{tabbing}
  @MM@\= @MM@ \= \kill
  @let@ trigger_fetch ($\textit{index}$: stream $\NN$): stream trigger = \\
    \> @contract@ \\
    \> \> \{ $0 \le \textit{index} \le \textit{maximum}$ \} \\
    \> \> Array.index_const \textit{triggers_array} \textit{index} \\
    \> \> \{ trigger.~$\true$ \} \\
\end{tabbing}
